---
title: "Transit_rate"
author: "Colby Hause"
date: "June 28, 2018"
output: html_document
---

Objective: create box and whisker plots that show transit rate of fish from one site to the immediate site downstream. the CSVs you want set up are:
group1_detections : all detections from group 1 fish, with columns: rel_group, date_tagged, Hex, GPS names, rkm, Genrkm (if you want), dtf, AND**** must include the upper release site (one detection for each tag at time of release)
group2_detections: all detections from group 2 fish, with columns: rel_group, date_tagged, Hex, GPS names, rkm, Genrkm (if you want), dtf, AND**** must include the Durham release site (one detection for each tag at time of release)
**make sure these detection files have has all bad detections REMOVED (predator dets
)
```{r}
library(tidyverse)
library(ggplot2)
library(readr)
```

First, set up your routes:
```{r}
#these are the routes for 2017:
group_one_routes <- c("Upstream Release Mainstem Route to Delta", "Upstream Release Paradise Cut Route", "Upstream Release Old River Route", "Upstream Release Mainstem Route")
group_two_routes <- c("Downstream Release Paradise Cut Route", "Downstream Release Old River Route", "Downstream Release Mainstem Route")
resto_routes <- c("Upstream Release Restoration Area Route")

```

Next, create a csv with the specific sites within each route. these are you df_locations in order route function
```{r}
#these are the df_locations for 2017
group1_locations <- read_csv("Z:/Shared/Projects/JSATS/DSP_Spring-Run Salmon/JSATS analysis/Tranist Rate Files/Group 1 receiver locations.csv")
group2_locations <- read_csv("Z:/Shared/Projects/JSATS/DSP_Spring-Run Salmon/JSATS analysis/Tranist Rate Files/Group 2 receiver locations.csv")
```

Use this function to change all individual receiver names to one site name. Run this function on group1_detections and group2_detections

```{r}
change_receiver_names <- function(df) {
  
  df$'GPS Names'[df$'GPS Names' == "CC_RGD_2_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CC_RGD_1_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CC_RGD_4_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CC_RGU1_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CC_RGU2_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CVP_Tank1_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CVP_Tank2_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CVP_Tank3_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CVP_Tank4_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CVPD_J"] <- "CC_CVP/RG"
  df$'GPS Names'[df$'GPS Names' == "CVPU_J"] <- "CC_CVP/RG"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_ParadiseCut_DN_1_3"] <- "SJ Paradise Cut"
  
  df$'GPS Names'[df$'GPS Names' == "Delt_ParadiseCut_1_J"] <- "Paradise Cut"
  df$'GPS Names'[df$'GPS Names' == "Delt_ParadiseCut_2_J"] <- "Paradise Cut"
  
  df$'GPS Names'[df$'GPS Names' == "Delt_TC_1_J"] <- "Turner Cut"
  df$'GPS Names'[df$'GPS Names' == "Delt_TC_2_J"] <- "Turner Cut"
  
  df$'GPS Names'[df$'GPS Names' == "ESB_Greenhouse Rd1_J"] <- "Greenhouse"
  df$'GPS Names'[df$'GPS Names' == "ESB_Greenhouse Rd2_J"] <- "Greenhouse"
  
  df$'GPS Names'[df$'GPS Names' == "ESB_Sandy Mush1_J"] <- "Sandy Mush"
  df$'GPS Names'[df$'GPS Names' == "ESB_Sandy Mush2_J"] <- "Sandy Mush"
  
  df$'GPS Names'[df$'GPS Names' == "Mar_Drain_1_J"] <- "Mariposa"
  df$'GPS Names'[df$'GPS Names' == "Mar_Drain_2_J"] <- "Mariposa"
  
  df$'GPS Names'[df$'GPS Names' == "MidR_hwy4_1_J"] <- "Mid R Hwy"  
  df$'GPS Names'[df$'GPS Names' == "MidR_hwy4_2_J"] <- "Mid R Hwy"
  df$'GPS Names'[df$'GPS Names' == "MidR_hwy4_3_J"] <- "Mid R Hwy"
  df$'GPS Names'[df$'GPS Names' == "MidR_hwy4_4_J"] <- "Mid R Hwy"
  
  df$'GPS Names'[df$'GPS Names' == "OR_HOR_1_J"] <- "OR Head OR"
  df$'GPS Names'[df$'GPS Names' == "OR_HOR_2_J"] <- "OR Head OR"
  df$'GPS Names'[df$'GPS Names' == "OR_HOR_3_J"] <- "OR Head OR"
  
  df$'GPS Names'[df$'GPS Names' == "OR_hwy4_2_J"] <- "OR Hwy"
  df$'GPS Names'[df$'GPS Names' == "OR_hwy4_3_J"] <- "OR Hwy"
  df$'GPS Names'[df$'GPS Names' == "OR_hwy4_4_J"] <- "OR Hwy"
  
  df$'GPS Names'[df$'GPS Names' == "OR_MidR_1_J"] <- "OR MR"
  df$'GPS Names'[df$'GPS Names' == "OR_MidR_2_J"] <- "OR MR"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_165_2_J"] <- "165"
  df$'GPS Names'[df$'GPS Names' == "SJ_165_1_J"] <- "165"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_BCA_1_J"] <- "BCA"
  df$'GPS Names'[df$'GPS Names' == "SJ_BCA_2_J"] <- "BCA"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_BlwCrowsLanding_1_J"] <- "Crows"
  df$'GPS Names'[df$'GPS Names' == "SJ_BlwCrowsLanding_2_J"] <- "Crows"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_BlwWGrayson_2_J"] <- "Grayson"
  df$'GPS Names'[df$'GPS Names' == "SJ_BlwWGrayson_1_J"] <- "Grayson"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_Durhamferry_1_J"] <- "Durham Ferry"
  df$'GPS Names'[df$'GPS Names' == "SJ_Durhamferry_2_J"] <- "Durham Ferry"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_Hills_1_J"] <- "Hills Ferry"
  df$'GPS Names'[df$'GPS Names' == "SJ_Hills_2_J"] <- "Hills Ferry"
  df$'GPS Names'[df$'GPS Names' == "SJ_Hills_RT"] <- "Hills Ferry"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_HOR_1_J"] <- "HOR"
  df$'GPS Names'[df$'GPS Names' == "SJ_HOR_2_J"] <- "HOR"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_Howard_1_J"] <- "Howard"
  df$'GPS Names'[df$'GPS Names' == "SJ_Howard_2_J"] <- "Howard"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_JP_1_J"] <- "Jersey Point"
  df$'GPS Names'[df$'GPS Names' == "SJ_JP_2_J"] <- "Jersey Point"
  df$'GPS Names'[df$'GPS Names' == "SJ_JP_3_J"] <- "Jersey Point"
  df$'GPS Names'[df$'GPS Names' == "SJ_JP_4_J"] <- "Jersey Point"
  df$'GPS Names'[df$'GPS Names' == "SJ_JP_5_J"] <- "Jersey Point"
  df$'GPS Names'[df$'GPS Names' == "SJ_JP_6_J"] <- "Jersey Point"
  df$'GPS Names'[df$'GPS Names' == "SJ_JP_7_J"] <- "Jersey Point"
  df$'GPS Names'[df$'GPS Names' == "SJ_JP_8_J"] <- "Jersey Point"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_MAC_1_J"] <- "MAC"
  df$'GPS Names'[df$'GPS Names' == "SJ_MAC_2_J"] <- "MAC"
  df$'GPS Names'[df$'GPS Names' == "SJ_MAC_3_J"] <- "MAC"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_MF1_J"] <- "Medford"
  df$'GPS Names'[df$'GPS Names' == "SJ_MF2_J"] <- "Medford"
  df$'GPS Names'[df$'GPS Names' == "SJ_MF3_J"] <- "Medford"
  df$'GPS Names'[df$'GPS Names' == "SJ_MF4_J"] <- "Medford"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_Moss_2_J"] <- "Mossdale"
  df$'GPS Names'[df$'GPS Names' == "SJ_Moss_1_J"] <- "Mossdale"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_SJC_1_J"] <- "SJC"
  df$'GPS Names'[df$'GPS Names' == "SJ_SJC_2_J"] <- "SJC"
  df$'GPS Names'[df$'GPS Names' == "SJ_SJC_3_J"] <- "SJC"
  df$'GPS Names'[df$'GPS Names' == "SJ_SJC_4_J"] <- "SJC"
  
  df$'GPS Names'[df$'GPS Names' == "SJ_SJG_1_J"] <- "SJG"
  df$'GPS Names'[df$'GPS Names' == "SJ_SJG_2_J"] <- "SJG"
  df$'GPS Names'[df$'GPS Names' == "SJ_SJG_3_J"] <- "SJG"
  df$'GPS Names'[df$'GPS Names' == "SJ_SJG_4_J"] <- "SJG"
  
  df$'GPS Names'[df$'GPS Names' == "Chipps1.1"] <- "Chipps"
  df$'GPS Names'[df$'GPS Names' == "Chipps1.2"] <- "Chipps"
  df$'GPS Names'[df$'GPS Names' == "Chipps1.3"] <- "Chipps"
  df$'GPS Names'[df$'GPS Names' == "Chipps1.4"] <- "Chipps"
  df$'GPS Names'[df$'GPS Names' == "Chipps1.5"] <- "Chipps"
  df$'GPS Names'[df$'GPS Names' == "Chipps2.1"] <- "Chipps"
  df$'GPS Names'[df$'GPS Names' == "Chipps2.2"] <- "Chipps"
  df$'GPS Names'[df$'GPS Names' == "Chipps2.3"] <- "Chipps"
  df$'GPS Names'[df$'GPS Names' == "Chipps2.4"] <- "Chipps"
  df$'GPS Names'[df$'GPS Names' == "Chipps2.5"] <- "Chipps"
  
  df$'GPS Names'[df$'GPS Names' == "GG1"] <- "Golden Gate"
  df$'GPS Names'[df$'GPS Names' == "GG2.1"] <- "Golden Gate"
  df$'GPS Names'[df$'GPS Names' == "GG3.1"] <- "Golden Gate"
  df$'GPS Names'[df$'GPS Names' == "GG4"] <- "Golden Gate"
  df$'GPS Names'[df$'GPS Names' == "GG5.1"] <- "Golden Gate"
  df$'GPS Names'[df$'GPS Names' == "GG6"] <- "Golden Gate"
  df$'GPS Names'[df$'GPS Names' == "GG7"] <- "Golden Gate"
  df$'GPS Names'[df$'GPS Names' == "GG7.5"] <- "Golden Gate"
  df$'GPS Names'[df$'GPS Names' == "GG8"] <- "Golden Gate"
  df$'GPS Names'[df$'GPS Names' == "GG9"] <- "Golden Gate"
  
  
  
  df$'GPS Names'[df$'GPS Names' == "Benicia1"] <- "Benicia"
  df$'GPS Names'[df$'GPS Names' == "Benicia2"] <- "Benicia"
  df$'GPS Names'[df$'GPS Names' == "Benicia3"] <- "Benicia"
  df$'GPS Names'[df$'GPS Names' == "Benicia4"] <- "Benicia"
  df$'GPS Names'[df$'GPS Names' == "Benicia5"] <- "Benicia"
  df$'GPS Names'[df$'GPS Names' == "Benicia6"] <- "Benicia"
  df$'GPS Names'[df$'GPS Names' == "Benicia7"] <- "Benicia"
  df$'GPS Names'[df$'GPS Names' == "Benicia8"] <- "Benicia"
  
  df$'GPS Names'[df$'GPS Names' == "AntiochBr09 "] <- "Antioch"
  df$'GPS Names'[df$'GPS Names' == "AntiochBr11 "] <- "Antioch"
  df$'GPS Names'[df$'GPS Names' == "AntiochBr13 "] <- "Antioch"
  df$'GPS Names'[df$'GPS Names' == "AntiochBr15 "] <- "Antioch"
  df$'GPS Names'[df$'GPS Names' == "AntiochBr17 "] <- "Antioch"
  df$'GPS Names'[df$'GPS Names' == "AntiochBr18 "] <- "Antioch"
  df$'GPS Names'[df$'GPS Names' == "AntiochBr19 "] <- "Antioch"
  df$'GPS Names'[df$'GPS Names' == "AntiochBr20 "] <- "Antioch"
  df$'GPS Names'[df$'GPS Names' == "AntiochN "] <- "Antioch"
  

  df$'GPS Names'[df$'GPS Names' == "DeckrIs4"] <- "Decker"
  df$'GPS Names'[df$'GPS Names' == "DeckrIs1"] <- "Decker"
  
  
  return(df)
}


```
 
Determine transit rate by calculating the rate of each detection line, but then selecting only the detections we want ( last detection at the first receiver and first detection at the second, then last detection at the second and first detection at the third, etc...) via an if statement.
Your two df_detections files will be CSVs from each release group (described at top)
The df from this function will be your df_transit in the order route function 
```{r}
get_transit_rate<- function(df_detections, rkm_low , rkm_high) { 
  df_transit <- NULL
  rkm_det <- subset(df_detections, rkm > rkm_low & rkm < rkm_high)
  all_tags <- unique(rkm_det$Hex)
  print(all_tags)
  for (tag1 in all_tags) {
    print(tag1)
    ind_tag <- subset(rkm_det, rkm_det$Hex == tag1)
    ind_tag <- ind_tag[order(ind_tag$dtf), ]
    all_tag_rows <- c(1:nrow(ind_tag))
    for (hex in all_tag_rows) {
      first_receiver <- ind_tag$`GPS Names`[hex] 
      first_rkm <- ind_tag$rkm[hex] 
      first_dtf <- ind_tag$dtf[hex]
      second_receiver <- ind_tag$`GPS Names`[hex +1]
      second_rkm <- ind_tag$rkm[hex +1]
      second_dtf <- ind_tag$dtf[hex +1]
      diff_rkm <- first_rkm - second_rkm
      diff_time <- as.numeric(difftime(as.character(second_dtf), as.character(first_dtf), units = "days"))
      if(hex == nrow(ind_tag)) {
        break
      }
      if(first_rkm != second_rkm & diff_rkm !=0 & diff_rkm > 1){
        transit_rate <- diff_rkm/diff_time
        df_transit <- rbind(df_transit, data.frame(tag1, first_receiver, second_receiver, first_rkm, second_rkm, first_dtf, second_dtf, transit_rate))
      }
    }
  }
  return(df_transit)
  df_transit_test <<- df_transit
}

#example usage:
#df_transit_group1<- get_transit_rate(group1_det, 0 , 500)
#df_transit_group2 <- get_transit_rate(group2_det, 0, 500)

```

This function will order your transit rate dataframe by route and locations within that route. Just input which route vector you want, the newly made transit rate df, the locations df you want, and pdf name
NOTE: if you gett his error: 
Error in `$<-.data.frame`(`*tmp*`, "transit_rate_final", value = c(46.2411511009295,  : 
  replacement has 5 rows, data has 3
  this means you have to change the row in which R is putting the n total above. 
  ex.: so you would have to change this 5 to a 3
  medians$transit_rate_final[5] <- 104

```{r}
order_route<- function(route_vector, transit_rate_df, locations_df, pdf_name) { 
  pdf(height = 8, width = 10, paste("Z://Shared//Projects//JSATS//DSP_Spring-Run Salmon//JSATS analysis//Tranist Rate Files//finalized_code_CH//", pdf_name, ".pdf", sep = ""))
  df_route <- NULL
  for (route in route_vector) {
    df_all_rates <- NULL
    loc_colname <- route
    print(loc_colname)
    number <- 1
    all_rows <- c(1:nrow(locations_df))
    #print("here")
    for (row in all_rows) {
      first <- locations_df[[loc_colname]][row]
      second <- locations_df[[loc_colname]][row + 1]
      print(first)
      print(second)
      print("here")
      df_route <- rbind(df_route, data.frame(first, second))
      if (is.na(first) == TRUE) {
        next
      }
      #print("here")
      #incorporate transit rate:
      one_move <- subset(transit_rate_df, grepl(first, transit_rate_df$first_receiver) & grepl(second, transit_rate_df$second_receiver))
      one_move_rows <- c(1:nrow(one_move))
      print(one_move_rows)
      if (nrow(one_move) > 0) {
        for (add_transit in one_move_rows) {
          number<- number
          name_to_name <- paste(first, "to", second)
          print(name_to_name)
          transit_rate_final <- one_move$transit_rate[add_transit]
          print("look here")
          df_all_rates <- rbind(df_all_rates, data.frame(first, second, name_to_name, transit_rate_final, number))
          df_new_rate <<- df_all_rates
        }
        number <- number +1
      }
    }
    print(df_all_rates)
    all_names <- unique(df_all_rates$name_to_name)
    df_total_number <- NULL
    for (name in all_names) {
      ind_number <- subset(df_all_rates, df_all_rates$name_to_name == name)
      total <- nrow(ind_number)
      df_total_number <- rbind(df_total_number, data.frame(name, total))
      print("this is the n:")
      print(df_total_number)
    }
    print("wtf")
    medians <- aggregate(transit_rate_final ~ name_to_name, data = df_all_rates, FUN = median)
    print("now here")
    last_medians <<- medians
    print("and here")
    #these if statements are specific to these sites, they place the "n" total right above the median line, just change the names and "n" values during different study years
    if (loc_colname == "2017 Lower Release Mainstem Route") {
      medians$transit_rate_final[5] <- 35
      medians$transit_rate_final[6] <- 25
    }
    if (loc_colname == "2017 Upper Release Mainstem Route") {
      medians$transit_rate_final[1] <- 10
      medians$transit_rate_final[5] <- 113
      medians$transit_rate_final[8] <- 25
      medians$transit_rate_final[9] <- 30
    }
    if (loc_colname == "Upstream Release Mainstem Route to Delta") {
      medians$transit_rate_final[3] <- 12.5
    }
    if (loc_colname ==  "Upstream Release Paradise Cut Route") {
      #medians$transit_rate_final[2] <- 69
      
    }
    if (loc_colname ==  "Upstream Release Mainstem Route") {
      #medians$transit_rate_final[4] <- 115
      medians$transit_rate_final[6] <- 27
      #medians$transit_rate_final[8] <- 29
    }
    if (loc_colname ==  "Downstream Release Paradise Cut Route") {
      #medians$transit_rate_final[3] <- 16
      #medians$transit_rate_final[3] <- 26
    }
    if (loc_colname ==  "Downstream Release Old River Route") {
      #medians$transit_rate_final[4] <- 43
      
    }
    if (loc_colname ==  "Downstream Release Mainstem Route") {
      #medians$transit_rate_final[6] <- 26
      #medians$transit_rate_final[8] <- 8.5
      medians$transit_rate_final[4] <- 75
      medians$transit_rate_final[7] <- 75
    }
    print("dog")
    if (loc_colname == "2017 Lower Release Mainstem Route") {
      transit_plot <- ggplot(data = df_all_rates, mapping = aes(x = name_to_name, y = transit_rate_final)) +
        geom_boxplot() +
        scale_x_discrete("Reach Movement") +
        scale_y_continuous(name = "Transit Rate (km/day)", breaks = seq(0,150,by=25), limits = c(0, 150)) +
        ggtitle(label = route) +
        theme(axis.text.x = element_text(angle = 45, hjust = .99, vjust = .99), text = element_text(size= 10)) +
        annotate("text", x = 1:length(unique(df_total_number$name)), y = medians$transit_rate_final +4 , label = df_total_number$total)
      plot(transit_plot)
    } 
    if (loc_colname == "Upstream Release Mainstem Route to Delta") {
      transit_plot <- ggplot(data = df_all_rates, mapping = aes(x = name_to_name, y = transit_rate_final)) +
        geom_boxplot() +
        scale_x_discrete("Reach Movement") +
        scale_y_continuous(name = "Transit Rate (km/day)", breaks = seq(0,150,by=25), limits = c(0, 150)) +
        ggtitle(label = route) +
        theme(axis.text.x = element_text(angle = 45, hjust = .99, vjust = .99), text = element_text(size=9)) +
        annotate("text", x = 1:length(unique(df_total_number$name)), y = medians$transit_rate_final +4 , label = df_total_number$total)
      plot(transit_plot)
    } else {
      
      transit_plot <- ggplot(data = df_all_rates, mapping = aes(x = name_to_name, y = transit_rate_final)) +
        geom_boxplot() +
        scale_x_discrete("Reach Movement") +
        scale_y_continuous(name = "Transit Rate (km/day)", breaks = seq(0,150,by=25), limits = c(0, 150)) +
        ggtitle(label = route) +
        theme(axis.text.x = element_text(angle = 45, hjust = .99, vjust = .99), text = element_text(size=11)) +
        annotate("text", x = 1:length(unique(df_total_number$name)), y = medians$transit_rate_final + 4 , label = df_total_number$total)
      plot(transit_plot)
    }
  }
  dev.off()
}




#example useage:
#group1_plots <- order_route(group_one_routes, df_transit_group1, group1_locations, pdf_name = 'group1 plot PDFs')
#group2_plots <- order_route(group_two_routes, df_transit_group2, group2_locations, pdf_name = 'group2 plot PDFs')

```
