---
title: "Diel Analysis"
author: "Colby Hause"
date: "July, 20, 2018"
output: html_document
---
Code update: 7/19/18:Made changes starting at line 162. Made loop iterate through GPS names instead of Genrkm. For some reason looping through Genrkm made it so each rkm was being assigned the first GPSname, not its actual. 
Also changed lines 192-194 to loops through these rec names instead of Genrkms


Objective: The two functions below will create circular histograms showing diel movement of fish. The circular histograms represent a clock with noon at the bottom and midnight at the top. Bars represent the number of fish detected during the night (blue) and day (red) for every hour of the day.

**FIRST: use change receiver names function to group recievers by GPS name (located in Transit Rate rmd)

The first function creates the directon and magnitude arrow for the dataset
The second function, make_cicular_plots, will output one plot for each site
The thirdfunction, make_circular_plots_multi, will output one plot for a group of specified sites

**NOTE: if you end up havig issues with colors of the plots (day night switching from red blue interchangably, look at how daynight is ordered ( line 268 and 435))

LOAD THESE:
```{r}
library(gridExtra)
library(RColorBrewer)
library(StreamMetabolism)
library(ggplot2)
```

This function conducts a Rayleigh's Test on the dataframe, obtaining a direction and magnitude of a arrow vector that will be displayed on the graph, adjusted according to the data:
```{r}
cc_rayleigh_test <- function(v_hour) {
azi <- function(hour) { #converts hours to degrees in a circle
  a <- (360*hour)/24
  return(a)
}

deg_to_rad <- function(degrees) {
  r <- degrees * pi / 180
}

rad_to_deg <- function(radians) {
  d <- radians * 180 / pi
}

cosine_a_vector <- function(some_vector) {
  #v should be c(1.570796, 3.141593, 4.712389, 6.283185)
  right_vector <- c()
  count <- 1
  for (v in some_vector) {
    right_vector[count] <- cos(signif(v, digits = 7))
    #print(cos(v))
    count <- count + 1
  }
  return(right_vector)
}
sin_a_vector <- function(some_vector) {
  #v should be c(1.570796, 3.141593, 4.712389, 6.283185)
  right_vector <- c()
  count <- 1
  for (v in some_vector) {
    right_vector[count] <- sin(signif(v, digits = 7))
    #print(cos(v))
    count <- count + 1
  }
  return(right_vector)
}

a_hour_degrees <- sapply(v_hour, azi)

a_hour_radians <- sapply(a_hour_degrees, deg_to_rad)

cos_hour <- cosine_a_vector(a_hour_radians)

sin_hour<- sin_a_vector(a_hour_radians)

sum_cos_hour <- sum(cos_hour)

sum_sin_hour <- sum(sin_hour)


Y <- sum_sin_hour/length(v_hour)
#print(Y)

X <- sum_cos_hour/length(v_hour)
#print(X)

r <- sqrt(X^2 + Y^2)
#print(paste("r value:", r))

sina <- Y/r

cosa <- X/r

p <- (length(v_hour)) * (r^2)
#print(paste("z Value:", p))


final_radian <- atan(sina/cosa)
direction <- rad_to_deg(final_radian)
direction <- abs(direction)
#print(direction)
if (Y > 0 & X > 0) {
  final_direction <- direction
}
if (Y > 0 & X < 0) {
  final_direction <- 180 - direction
}
if (Y < 0 & X < 0) {
  final_direction <- 180 + direction
}
if (Y < 0 & X > 0) {
  final_direction <- 360 - direction
}
final_output <- c(final_direction, r)
return(final_output)
}

######################

degrees2hours <- function(degrees) { #converts degrees to hours in a circle on a 24 hr clock
  hour <- 24*degrees/360
  return(hour) 
}

makeColors <- function(){
  maxColors <- 3
  usedColors <- c()
  possibleColors <- colorRampPalette(brewer.pal( 3 , "Set1" ) )(maxColors)
  
  function(values){
    newKeys <- setdiff(values, names(usedColors))
    newColors <- possibleColors[1:length(newKeys)]
    usedColors.new <-  c(usedColors, newColors)
    names(usedColors.new) <- c(names(usedColors), newKeys)
    usedColors <<- usedColors.new
    
    possibleColors <<- possibleColors[length(newKeys)+1:maxColors]
    usedColors
  }
} 

#mkColor <- makeColors()

```


This function will output one circular histogram plot per "site". These sites are groups by general rkm, so that 4 recievers at one location are all grouped and considered one site. 
df_detections = a csv of all you detections after you have run them through a predator filter/ gone through each rkm plot and deleted the bad detection out of the access database. In the csv include the columns: RecSN, dtf, Hex, GPS Names, Genrkm, and Rel_group. You will most like run two csvs through this function, group 1 and group 2
*only difference bewteen this code and the 2017 code is this code used the Gen_name col instead of using the change receivers function and therefore pulling from the GPS names col
```{r}
make_circular_plots <- function(df_detections, pdf_name) {
  pdf(paste(pdf_name, ".pdf", sep = "" ))
  red_blue <- scales::seq_gradient_pal('red', 'blue')(seq(0,1,length.out=2))
  df_initial_detections <- NULL
  all_tags <- unique(df_detections$Hex)
  #rec_names <- unique(df_detections$Gen_Name)
  for (tag in all_tags) {                     # Tells the loop that it is going to pull out the rows of the det dfs based on the list in the AllTags vector (starting with first tag)
    #print(tag)                              # prints the tag you are on
    ind_tag <- subset(df_detections, df_detections$Hex == tag)     # Takes the hex column in df det, pulls out the rows of the tag code for that iteration- assigns this to df ind_tag
    allrkm <- unique(ind_tag$Genrkm)
    print(allrkm)
    rec_names <- unique(ind_tag$Gen_Name)
    print(rec_names)
    if (nrow(ind_tag) > 0) {                   # continues loop if there is a tag detection present 
      for(name in rec_names) {                  # Tells the loop to pull out rows grouped by GPS name from whatever tag it is on in the AllTags vector 
        #print(rkm)                       # Prints the GPS name that is on
        ind_rec <- subset(ind_tag, ind_tag$Gen_Name == name)  #Tells the loop to pull out rows grouped by GPS name from whatever tag it is on in the AllTags vector- puts into df ind_rec
        rec_name <- ind_rec$Gen_Name[1]
        print(rec_name)
        if (nrow(ind_rec) > 0) {                   # Stops Loop if there is no detection at site
          first_det <- min(ind_rec$dtf)              # takes only the the min dtf in df ind_rec, which is the first detection of that tage at that site
          group <- ind_rec$Rel_group[1]           #takes the release group of the tag
          Genrkm <- ind_rec$Genrkm[1]
          #for (rec in rec_names) {
          #print(rec)
          #receiver <- subset(df_detections, df_detections$Gen_Name == rec)
          #print(receiver)
          #}
          df_initial_detections = rbind(df_initial_detections, data.frame(group, rec_name, tag, Genrkm, first_det))    #Appends all data to df_Grp1/2 Detects
        }
      }
    }
  }
  df_initial_detections_test <<- df_initial_detections
  
  #this line rounds df_initial_detections to the nearest hour:
  df_initial_detections$round_det <- format(round(df_initial_detections$first_det, units = "hours"), format ="%H")
  test_df <<- df_initial_detections
  
  
  #Now we have a data.frame with the receiver and first time (rounded)
  #Need to determine the number of instances (detections) associated with each site.
  l_all_names <- unique(df_initial_detections$rec_name)
  # site should go to rkm and df_firsttime <- df initital dets
  for (n in l_all_names) {
    print(n)
    test_site <- subset(df_initial_detections, rec_name == n)
    receiver <- test_site$rec_name[1]        # pulls out receiver name for title of plot in ggplot
    print(receiver)
    #receiver <- substr(receiver,1, nchar(as.character(receiver))-4)     # all this does is take off the _#_J in the title of receiver 
    #test_site$rounded_time <- as.numeric(as.character(test_site$rounded_time)) #changes column of test_site to numeric values
    unique_tags <- unique(test_site$tag)
    pre_df_num_instances <- NULL
    #all_hours <- unique(test_site$rounded_time)
    all_tags <- unique(test_site$tag)
    #print(nrow(test_site))
    if (nrow(test_site) > 0) {
      first_date <- min(test_site$first_det)
      last_date <- max(test_site$first_det)
      
      mid_date <- as.POSIXct((as.numeric(first_date) + as.numeric(last_date))/2, origin = '1970-01-01')
      format_middle_date <- format(mid_date, '%Y/%m/%d')
      df_sunrise_sunset <- sunrise.set(lat = 37.9577, long = -121.2908, timezone = "America/Los_Angeles", date = format_middle_date) #GPS Points are for STOCKTON
      rounded_sunrise <- format(round(df_sunrise_sunset$sunrise[1], units = "hours"), format ="%H")
      rounded_sunset <- format(round(df_sunrise_sunset$sunset[1], units = "hours"), format ="%H")
      
      for (t in all_tags) {
        #print(hour)
        #ind_hour <- subset(test_site, rounded_time == hour)
        ind_tag <- subset(test_site, tag == t)
        min_hour <- min(ind_tag$round_det)
        pre_df_num_instances = rbind(pre_df_num_instances, data.frame(t, min_hour))
      }
      #print("HERE")
      
      #print(pre_df_num_instances)
      pre_df_num_instances$min_hour <- as.integer(as.character(pre_df_num_instances$min_hour))
      all_hours <- c(unique(pre_df_num_instances$min_hour))
      
      df_num_instances <- NULL
      for (hour in all_hours) {
        #print(hour)
        #print(class(hour))
        daynight <- NA
        ind_hour <- subset(pre_df_num_instances, min_hour == hour)
        ind_number <- length(unique(ind_hour$t))  
        int_sunrise <- as.integer(rounded_sunrise)
        int_sunset <- as.integer(rounded_sunset)
        #print('Sunrise and Sunset')
        #print(int_sunrise)
        #print(class(int_sunrise))
        #print(int_sunset)
        #print(class(int_sunset))
        if (hour >= int_sunrise & hour <= int_sunset) { #if hour >= 6 and hour <= 19
          daynight <- "Day"
          df_num_instances = rbind(df_num_instances, data.frame(hour, ind_number, daynight))
          
        }
        else {
          daynight <- "Night"
          #print(daynight)
          df_num_instances = rbind(df_num_instances, data.frame(hour, ind_number, daynight))
        }
      }
      #print(df_num_instances)
      hour_vector <- c(pre_df_num_instances$min_hour)  #This is the vector we use to determine rayleighs r vector
      #print(hour_vector)
      #print("here")
      ray_vector <- cc_rayleigh_test(hour_vector)
      #print("here")
      x_position <- degrees2hours(ray_vector[1])
      magnitude <- ray_vector[2]
      df_ray <- data.frame(x_position, magnitude)
      
      
      df_day <- subset(df_num_instances, daynight == "Day")
      df_night <- subset(df_num_instances, daynight == "Night")
      day_number <- sum(df_day$ind_number)
      night_number <- sum(df_night$ind_number)
      total_number <- sum(df_num_instances$ind_number)
      #df_night_test <<- df_night
      
      #print(paste("Plotting Circular Graph for", site))
      
      df_num_instances$hour[df_num_instances$hour == 0] <- 24
      df_num_instances_test <<- df_num_instances
      df_num_instances$daynight <- as.character(df_num_instances$daynight)
      #df_num_instances<- arrange(df_num_instances,  (daynight))
      df_num_instances <- df_num_instances[order(df_num_instances$daynight, decreasing = FALSE), ]
      #print(df_num_instances)
      
      #ind_number should be the number of total detections at an hour
      
      if (max(df_num_instances$ind_number) <= 20) {
        circular_plot <- ggplot(df_num_instances, aes(x=factor(hour), y = ind_number, fill = daynight)) + geom_bar(stat = "identity") +
          geom_hline(yintercept = seq(0,max(df_num_instances$ind_number), by = 1)) +
          geom_segment(data = df_ray, aes(x = x_position, y = 0, xend = x_position, yend = magnitude * max(df_num_instances$ind_number)), arrow = arrow(type = "closed", length = unit(.2, "cm"))) +
          coord_polar(theta = "x", start = .13) +
          scale_x_discrete("Hour", limits = c(1:24), breaks = seq(1, 24, by=1)) +
          scale_y_continuous("Number of Fish" , breaks = seq(0, max(df_num_instances$ind_number), by=1)) +
          ggtitle(receiver) +
          labs(fill = paste("N = ", length(unique_tags), '\n', round(day_number/total_number*100), '% Day', '\n', round(night_number/total_number*100), "% Night")) +
          scale_fill_manual(values = red_blue )
        plot(circular_plot)
      }
      
      if (max(df_num_instances$ind_number) > 20 & max(df_num_instances$ind_number) <= 50){
        circular_plot <- ggplot(df_num_instances, aes(x=factor(hour), y = ind_number, fill = daynight)) + geom_bar(stat = "identity") +
          geom_hline(yintercept = seq(0,max(df_num_instances$ind_number), by = 2)) +
          geom_segment(data = df_ray, aes(x = x_position, y = 0, xend = x_position, yend = magnitude * max(df_num_instances$ind_number)), arrow = arrow(type = "closed", length = unit(.2, "cm"))) +
          coord_polar(theta = "x", start = .13) +
          scale_x_discrete("Hour", limits = c(1:24), breaks = seq(1, 24, by=1)) +
          scale_y_continuous("Number of Fish" , breaks = seq(0, max(df_num_instances$ind_number), by=2)) +
          ggtitle(receiver) +
          labs(fill = paste("N = ", length(unique_tags), '\n', round(day_number/total_number*100), '% Day', '\n', round(night_number/total_number*100), "% Night")) +
          scale_fill_manual(values = red_blue )
        plot(circular_plot)
      }
      
      if (max(df_num_instances$ind_number) > 75) {
        #print(magnitude)
        #print(max(df_num_instances$ind_number))
        circular_plot <- ggplot(df_num_instances, aes(x=factor(hour), y = ind_number, fill = daynight)) + geom_bar(stat = "identity") +
          geom_hline(yintercept = seq(0,max(df_num_instances$ind_number), by = 25)) +
          geom_segment(data = df_ray, aes(x = x_position, y = 0, xend = x_position, yend = magnitude * max(df_num_instances$ind_number)), arrow = arrow(type = "closed", length = unit(.2, "cm"))) +
          coord_polar(theta = "x", start = .13) +
          scale_x_discrete("Hour", limits = c(1:24), breaks = seq(1, 24, by=1)) +
          scale_y_continuous("Number of Fish" , breaks = seq(0, max(df_num_instances$ind_number), by=25)) +
          ggtitle(receiver) +
          labs(fill = paste("N = ", length(unique_tags), '\n', round(day_number/total_number*100), '% Day', '\n', round(night_number/total_number*100), "% Night")) +
          scale_fill_manual(values = red_blue)
        plot(circular_plot)
      }
    }
  }
  dev.off()
}



```


Run-through code:
```{r}
#make_circular_plots(#df with all detections, pdf_name = "All Sites")
group1_2018_ind_plot <- make_circular_plots(group1_16rkm_2018, pdf_name = "2018 All Sites Group1")
group2_2018_ind_plot <- make_circular_plots(group2_16rkm_2018, pdf_name = "2018 All Sites Group2")

```


This function will make one plot for multiple sites combined, for example, restoration area sites or delta sites. 
df_detections = a subset of you master detection file by the site that you want.

Changes made on 8/13/18: line 407: changed dets from only unique tags to dets from all tags
Changed first chunk of code so that ind_rec subsets by Gen_Name not Genrkm. Subsetting by Genrkm was allowing dets to be kept from both recievers at one location (ie hills 1 and 2) instead of pooling those dets and just picking the first one. 
```{r}
make_circular_plots_multi <- function(df_detections, pdf_name, group_title) {
  pdf(paste(pdf_name, ".pdf", sep = "" ))
  red_blue <- scales::seq_gradient_pal('red', 'blue')(seq(0,1,length.out=2))
  df_initial_detections <- NULL
  all_tags <- unique(df_detections$Hex)
  for (tag in all_tags) { # Tells the loop that it is going to pull out the rows of the det dfs based on the list in the AllTags vector (starting with first tag)
    print(tag)                              # prints the tag you are on
    ind_tag <- subset(df_detections, df_detections$Hex == tag)     # Takes the hex column in df det, pulls out the rows of the tag code for that iteration- assigns this to df ind_tag
    all_names <- unique(ind_tag$Gen_Name)
    if (nrow(ind_tag) > 0) {                   # continues loop if there is a tag detection present 
      for(name in all_names) {                  # Tells the loop to pull out rows grouped by GPS name from whatever tag it is on in the AllTags vector 
        print(name)                       # Prints the GPS name that is on
        ind_rec <- subset(ind_tag, ind_tag$Gen_Name == name)  #Tells the loop to pull out rows grouped by GPS name from whatever tag it is on in the AllTags vector- puts into df ind_rec
        if (nrow(ind_rec) > 0) {                   # Stops Loop if there is no detection at site
          first_det <- min(ind_rec$dtf)              # takes only the the min dtf in df ind_rec, which is the first detection of that tage at that site
          group <- ind_rec$Rel_group[1]           #takes the release group of the tag
          Genrkm <- ind_rec$Genrkm[1]
          df_initial_detections = rbind(df_initial_detections, data.frame(group, tag, Genrkm, first_det))    #Appends all data to df_Grp1/2 Detects
        }
      }
    }
  }
  df_initial_detections_test <<- df_initial_detections
  
  
  #this line rounds df_initial_detections to the nearest hour:
  df_initial_detections$round_det <- format(round(df_initial_detections$first_det, units = "hours"), format ="%H")
  test_df <<- df_initial_detections
  
  
  #Now we have a data.frame with the receiver and first time (rounded)
  #Need to determine the number of instances (detections) associated with each site.
  
  # site should go to rkm and df_firsttime <- df initital dets
  test_site <- df_initial_detections
  #test_site$rounded_time <- as.numeric(as.character(test_site$rounded_time)) #changes column of test_site to numeric values
  unique_tags <- unique(test_site$tag)
  #all_hours <- unique(test_site$rounded_time)
  all_tags <- unique(test_site$tag)
  #print(nrow(test_site))
  if (nrow(test_site) > 0) {
    first_date <- min(test_site$first_det)
    last_date <- max(test_site$first_det)
    
    mid_date <- as.POSIXct((as.numeric(first_date) + as.numeric(last_date))/2, origin = '1970-01-01')
    format_middle_date <- format(mid_date, '%Y/%m/%d')
    df_sunrise_sunset <- sunrise.set(lat = 37.9577, long = -121.2908, timezone = "America/Los_Angeles", date = format_middle_date) #GPS Points are for STOCKTON
    rounded_sunrise <- format(round(df_sunrise_sunset$sunrise[1], units = "hours"), format ="%H")
    rounded_sunset <- format(round(df_sunrise_sunset$sunset[1], units = "hours"), format ="%H")
    
    
    #print(df_initial_detections)
    df_initial_detections$round_det <- as.integer(as.character(df_initial_detections$round_det))
    all_hours <- c(unique(df_initial_detections$round_det))
    
    df_num_instances <- NULL
    for (hour in all_hours) {
      print(hour)
      print(class(hour))
      daynight <- NA
      ind_hour <- subset(df_initial_detections, round_det == hour)
      #ind_number <- length(unique(ind_hour$t))  this would only take the first det of a tag at a site and ignore its detections at other sites in the group
      ind_number <- nrow(ind_hour)
      int_sunrise <- as.integer(rounded_sunrise)
      int_sunset <- as.integer(rounded_sunset)
      print('Sunrise and Sunset')
      print(int_sunrise)
      print(class(int_sunrise))
      print(int_sunset)
      print(class(int_sunset))
      if (hour >= int_sunrise & hour <= int_sunset) { #if hour >= 6 and hour <= 19
        daynight <- "Day"
        df_num_instances = rbind(df_num_instances, data.frame(hour, ind_number, daynight))
        
      }
      else {
        daynight <- "Night"
        #print(daynight)
        df_num_instances = rbind(df_num_instances, data.frame(hour, ind_number, daynight))
      }
    }
    #print(df_num_instances)
    #print("here")
    hour_vector <- c(df_initial_detections$round_det)  #This is the vector we use to determine rayleighs r vector
    print(hour_vector)
    print("here")
    ray_vector <- cc_rayleigh_test(hour_vector)
    #print("here")
    x_position <- degrees2hours(ray_vector[1])
    magnitude <- ray_vector[2]
    df_ray <- data.frame(x_position, magnitude)
    
    
    df_day <- subset(df_num_instances, daynight == "Day")
    df_night <- subset(df_num_instances, daynight == "Night")
    day_number <- sum(df_day$ind_number)
    night_number <- sum(df_night$ind_number)
    total_number <- sum(df_num_instances$ind_number)
    
    #print(paste("Plotting Circular Graph for", site))
    
    df_num_instances$hour[df_num_instances$hour == 0] <- 24
    df_num_instances$daynight <- as.character(df_num_instances$daynight)
    #df_num_instances<- arrange(df_num_instances, desc(daynight))
    df_num_instances <- df_num_instances[order(df_num_instances$daynight, decreasing = FALSE), ]
    print("this is the total number of instances:")
    print(total_number)
    
    #ind_number should be the number of total detections at an hour
    
    if (max(df_num_instances$ind_number) <= 20) {
      circular_plot <- ggplot(df_num_instances, aes(x=factor(hour), y = ind_number, fill = daynight)) + geom_bar(stat = "identity") +
        geom_hline(yintercept = seq(0,max(df_num_instances$ind_number), by = 1)) +
        geom_segment(data = df_ray, aes(x = x_position, y = 0, xend = x_position, yend = magnitude * max(df_num_instances$ind_number)), arrow = arrow(type = "closed", length = unit(.2, "cm"))) +
        coord_polar(theta = "x", start = .13) +
        scale_x_discrete("Hour", limits = c(1:24), breaks = seq(1, 24, by=1)) +
        scale_y_continuous("Number of Fish" , breaks = seq(0, max(df_num_instances$ind_number), by=1)) +
        ggtitle(group_title) +
        labs(fill = paste("N = ", length(unique_tags), '\n', round(day_number/total_number*100), '% Day', '\n', round(night_number/total_number*100), "% Night")) +
        scale_fill_manual(values = red_blue)
      plot(circular_plot)
    }
    
    if (max(df_num_instances$ind_number) > 20 & max(df_num_instances$ind_number) <= 50){
      circular_plot <- ggplot(df_num_instances, aes(x=factor(hour), y = ind_number, fill = daynight)) + geom_bar(stat = "identity") +
        geom_hline(yintercept = seq(0,max(df_num_instances$ind_number), by = 10)) +
        geom_segment(data = df_ray, aes(x = x_position, y = 0, xend = x_position, yend = magnitude * max(df_num_instances$ind_number)), arrow = arrow(type = "closed", length = unit(.2, "cm"))) +
        coord_polar(theta = "x", start = .13) +
        scale_x_discrete("Hour", limits = c(1:24), breaks = seq(1, 24, by=1)) +
        scale_y_continuous("Number of Fish" , breaks = seq(0, max(df_num_instances$ind_number), by=10)) +
        ggtitle(group_title) +
        labs(fill = paste("N = ", length(unique_tags), '\n', round(day_number/total_number*100), '% Day', '\n', round(night_number/total_number*100), "% Night")) +
        scale_fill_manual(values = red_blue)
      plot(circular_plot)
    }
    
    if (max(df_num_instances$ind_number) > 50) {
      print(magnitude)
      print(max(df_num_instances$ind_number))
      circular_plot <- ggplot(df_num_instances, aes(x=factor(hour), y = ind_number, fill = daynight)) + geom_bar(stat = "identity") +
        geom_hline(yintercept = seq(0,max(df_num_instances$ind_number), by = 25)) +
        geom_segment(data = df_ray, aes(x = x_position, y = 0, xend = x_position, yend = magnitude * max(df_num_instances$ind_number)), arrow = arrow(type = "closed", length = unit(.2, "cm"))) +
        coord_polar(theta = "x", start = .13) +
        scale_x_discrete("Hour", limits = c(1:24), breaks = seq(1, 24, by=1)) +
        scale_y_continuous("Number of Fish" , breaks = seq(0, max(df_num_instances$ind_number), by=25)) +
        ggtitle(group_title) +
        labs(fill = paste("N = ", length(unique_tags), '\n', round(day_number/total_number*100), '% Day', '\n', round(night_number/total_number*100), "% Night")) +
        scale_fill_manual(values = red_blue)
      plot(circular_plot)
    }
  }
  dev.off()
}

```

Run through code:
```{r}
#make subsetted detection file:
df_detections = titleofgroup <- subset(#full detection file, Genrkm == | Genrkm == | etc.. )
  
make_circular_plots_multi(#subsetted detection file, "pdf name", "title of group of receivers")
  
  
#These are the groups we made for the preliminary 2018 data: 
                                                 resto_dets_1<- subset(group1_16rkm_2018, group1_16rkm_2018$Gen_Name == "Blw Release" | group1_16rkm_2018$Gen_Name == "Mud SL Br" | 
                        group1_16rkm_2018$Gen_Name == "Mud SL Conf" | group1_16rkm_2018$Gen_Name == "Blw Newman") 
length(unique(resto_dets_1$Hex))

exit_resto_1 <- subset(group1_16rkm_2018, group1_16rkm_2018$Gen_Name == "Hills Ferry" | group1_16rkm_2018$Gen_Name == "Hills RT")
length(unique(exit_resto_1$Hex))

lower_SJ_1 <- subset(group1_16rkm_2018, group1_16rkm_2018$Gen_Name == "Grayson" | group1_16rkm_2018$Gen_Name == "Crows" )
length(unique(lower_SJ_1$Hex))

enter_delta_1 <- subset(group1_16rkm_2018, group1_16rkm_2018$Gen_Name == "Durham Ferry")
length(unique(enter_delta_1$Hex))

delta_all_1 <- subset(group1_16rkm_2018, group1_16rkm_2018$Gen_Name == "BCA" | group1_16rkm_2018$Gen_Name == "Mossdale" |
                        group1_16rkm_2018$Gen_Name ==  "Head OR" | group1_16rkm_2018$Gen_Name == "OR Head OR" |
                        group1_16rkm_2018$Gen_Name == "MR OR" | 
                        group1_16rkm_2018$Gen_Name ==  " OR MR" | group1_16rkm_2018$Gen_Name ==  "CC_CVP/RG" |
                        group1_16rkm_2018$Gen_Name == "Howard" | group1_16rkm_2018$Gen_Name ==  "Mid R Hwy" |
                        group1_16rkm_2018$Gen_Name ==  "OR Hwy" | group1_16rkm_2018$Gen_Name ==  "SJG" |
                        group1_16rkm_2018$Gen_Name == "SJC" | group1_16rkm_2018$Gen_Name == " TC " |
                        group1_16rkm_2018$Gen_Name ==  "MAC" | group1_16rkm_2018$Gen_Name == "Medford" |
                        group1_16rkm_2018$Gen_Name ==  "Jersey Point") # | group1_16rkm_2018$Gen_Name == "Antioch" |
                        #group1_16rkm_2018$Gen_Name == "Decker")
length(unique(delta_all_1$Hex))

#exit_delta_1 <- subset(group1_16rkm_2018, group1_16rkm_2018$Gen_Name ==  "Chipps")
#length(unique(exit_delta_1$Hex))

#bay_1 <- subset(group1_16rkm_2018, group1_16rkm_2018$Gen_Name == "Benicia")
#length(unique(bay_1$Hex))

#enter_ocean_1<- subset(group1_16rkm_2018, group1_16rkm_2018$Gen_Name == "Golden Gate")
#length(unique(enter_ocean_1$Hex))

#GROUP2 FISH

enter_delta_2 <- subset(group2_16rkm_2018, group2_16rkm_2018$Gen_Name == "Durham Ferry")
length(unique(enter_delta_2$Hex))

delta_all_2 <- subset(group2_16rkm_2018, group2_16rkm_2018$Gen_Name == "BCA" | group2_16rkm_2018$Gen_Name == "Mossdale" |
                        group2_16rkm_2018$Gen_Name ==  "Head OR" | group2_16rkm_2018$Gen_Name == "OR Head OR" |
                        group2_16rkm_2018$Gen_Name == "MR OR" | 
                        group2_16rkm_2018$Gen_Name ==  " OR MR" | group2_16rkm_2018$Gen_Name ==  "CC_CVP/RG" |
                        group2_16rkm_2018$Gen_Name == "Howard" | group2_16rkm_2018$Gen_Name ==  "Mid R Hwy" |
                        group2_16rkm_2018$Gen_Name ==  "OR Hwy" | group2_16rkm_2018$Gen_Name ==  "SJG" |
                        group2_16rkm_2018$Gen_Name == "SJC" | group2_16rkm_2018$Gen_Name == " TC " |
                        group2_16rkm_2018$Gen_Name ==  "MAC" | group2_16rkm_2018$Gen_Name == "Medford" |
                        group2_16rkm_2018$Gen_Name ==  "Jersey Point") # | group2_16rkm_2018$Gen_Name == "Antioch" |
#group2_16rkm_2018$Gen_Name == "Decker")
length(unique(delta_all_2$Hex))

#exit_delta_2 <- subset(group2_16rkm_2018, group2_16rkm_2018$Gen_Name ==  "Chipps")
#length(unique(exit_delta_2$Hex))

#bay_2 <- subset(group2_16rkm_2018, group2_16rkm_2018$Gen_Name == "Benicia")
length(unique(bay_2$Hex))

#enter_ocean_2 <- subset(group2_16rkm_2018, group2_16rkm_2018$Gen_Name == "Golden Gate")
#length(unique(enter_ocean_2$Hex))



#MULTI-SITE PLOTS:

#GROUP1 FISH
make_circular_plots_multi(resto_dets_1, pdf_name = "2018 Group 1 Restoration Area", " 2018 Group 1 Fish through Restoration Area")
make_circular_plots_multi(exit_resto_1, pdf_name = "2018 Group 1 Exit Resto", "2018 Group 1 Fish exiting Restoration Area")
make_circular_plots_multi(lower_SJ_1, pdf_name = "2018 Group 1 Lower SJ", "2018 Group 1 Fish through the Lower San Joaquin")
make_circular_plots_multi(enter_delta_1, pdf_name = "2018 Group 1 Entering Delta", "2018 Group 1 Fish entering Delta")
make_circular_plots_multi(delta_all_1, pdf_name = "2018 Group 1 through Delta", "2018 Group 1 Fish through Delta")
#make_circular_plots_multi(exit_delta_1, pdf_name = "2018 Group 1 Exit Delta", "2018 Group 1 Fish exiting Delta")
#make_circular_plots_multi(bay_1, pdf_name = "2018 Group 1 Bay", "2018 Group 1 Fish through Bay")
#make_circular_plots_multi(enter_ocean_1, pdf_name = "2018 Group 1 Enter Ocean", "2018 Group 1 Fish entering Ocean")


#GROUP 2 FISH
make_circular_plots_multi(enter_delta_2, pdf_name = "2018 Group 2 Entering Delta", "2018 Group 2 Fish entering Delta")
make_circular_plots_multi(delta_all_2, pdf_name = "2018 Group 2 through Delta", "2018 Group 2 Fish through Delta")
#make_circular_plots_multi(exit_delta_2, pdf_name = "2018 Group 2 Exit Delta", "2018 Group 2 Fish exiting Delta")
#make_circular_plots_multi(bay_2, pdf_name = "2018 Group 2 Bay", "2018 Group 2 Fish through Bay")
#make_circular_plots_multi(enter_ocean_2, pdf_name = "2018 Group 2 Enter Ocean", "2018 Group 2 Fish entering Ocean")



```

