---
title: "Waterfall Plots"
author: "Colby Hause"
date: "June 26, 2018"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)

```

First: From access make a query that pulls: Relative group, date tagged, Hex, RecSN, GPS Names, rKM, and dtf and save as a csv- name this [year]AllFishGroups. 

Function to plot rkm over time of ech fish from specified group. All rkm plots will show up on one graph.
df = your dataframe of fish by group
df_tag_list = your dataframe again, unless you want to look at specific tags, then upload another list
```{r setup, include=FALSE}

plot_all_rkm_time_jsats <- function(df, df_tag_list,tag_colname, str_start_datetime, str_end_datetime, high_rkm, low_rkm, pdf_name, gg_title, file_location, initial_rkm = 0) {
  pdf(paste(file_location, pdf_name, ".pdf", sep = "" )) 
  #df_edit <- subset(df, rkm > initial_rkm)   use this line for reguar rkm
  df_edit <- subset(df, Genrkm > initial_rkm)
  df_edit <- subset(df_edit, dtf > str_start_datetime & dtf < str_end_datetime)
  all_tags <- unique(df_tag_list[[tag_colname]])
  df_edit_time <- df_edit[order(df_edit$dtf), ]
  first_time <- df_edit_time$dtf[1]
  last_time <- df_edit_time$dtf[nrow(df_edit_time)]
  first_det <- df_edit$dtf[1]
  last_det <- df_edit$dtf[nrow(df_edit)]
  
  #fish_move <- ggplot(df_edit, aes(x=dtf, y=rkm, color = Hex)) +  use this line for regular rkm
  fish_move <- ggplot(df_edit, aes(x=dtf, y=Genrkm, color = Hex)) +
    geom_point(size = .25) + geom_line(size = .25) +
    ggtitle(paste(gg_title)) +
    xlab("Time After Release") +
    #ylab("River Kilometer") +
    theme(plot.title = element_text(size = 10), legend.position = "none") +
    scale_x_datetime(date_breaks = "5 days") +
    scale_y_discrete(name = "River Kilometer", limits = seq(low_rkm, high_rkm, by=10)) +
    coord_cartesian(ylim = c(low_rkm, high_rkm)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  plot(fish_move)
  dev.off()
}


#example of set up for plot_all_rkm_time_jsats function:
#plot_all_rkm_time_jsats(new_group1, new_group1, tag_colname = "Hex", str_start_datetime="2017-01-01 00:00:00", str_end_datetime="2018-01-01 #00:00:00",low_rkm = 0, high_rkm = 320, pdf_name = "No Upstream over 12 km group 1", gg_title = "Upstream Release All Transmitters", #file_location = "Z://Shared//Projects//JSATS//DSP_Spring-Run Salmon//JSATS analysis//Waterfall Plots//")

#plot_all_rkm_time_jsats(new_group2, new_group2, tag_colname = "Hex", str_start_datetime="2017-01-01 00:00:00", str_end_datetime="2018-01-01 #00:00:00",low_rkm = 0, high_rkm = 190, pdf_name = "No Upstream over 12 km group 2", gg_title = "Upstream Release All Transmitters", #file_location = "Z://Shared//Projects//JSATS//DSP_Spring-Run Salmon//JSATS analysis//Waterfall Plots//")
```


To make individualrkm plots that will save as their own pdf into a specified folder:

```{r}
print_tags <- function(df, pdf_name) {
  pdf(paste(pdf_name, ".pdf"))  # this opens the pdf
  all_tags <- unique(df$Hex)
  for (tag in all_tags) {
    single_tag<- df %>% 
      filter(Hex == tag) 
      #p<-  ggplot(data = single_tag, aes(x = dtf, y = rkm)) + use this line for regular rkm
      p<-  ggplot(data = single_tag, aes(x = dtf, y = Genrkm)) +
      geom_point() +
      geom_line() +
      ggtitle(tag)
    plot(p)
  }
  dev.off()     # this closes the pdf
}
```

To make your diferent "group dataframes, filter out the release groups you want from the master FishByGroup csv. 

```{r}
allgroups <- read.csv( "file path of where your [year]AllFishGroups is")

group1 <- allgroups %>% 
  filter(Rel_group == "2017_SJ_SCARF1" | Rel_group == "2017_SJ_SIRF1" )

group2 <- allgroups %>% 
  filter(Rel_group == "2017_SJ_SCARF2" | Rel_group == "2017_SJ_SIRF2" )


```

